---
title: "Case Study 3 Model Variants"
output: 
  pdf_document: default
  html_document: default
---

```{r message = FALSE}
library(caret) #6.0-86
library(dplyr) #0.8.5
library(randomForest) #4.6-14
library(MASS) #7.3-51.5
library(matrixStats) #0.56.0
library(dplyr) #0.8.5
library(ggraph) #2.0.3
library(igraph) #1.2.5
library(cvAUC) #1.1.0
```

```{r}
load("final_data.rda")

new_data <- data.frame(new_data)

# Not stress is 1, stress is 2
new_data$label[new_data$label == 3] <- 1
new_data$label[new_data$label == 4] <- 1

# Stress is 1, Not-stress is 0
new_data$label[new_data$label == 1] <- 0
new_data$label[new_data$label == 2] <- 1

data <- data.frame(new_data)
data$label = as.factor(data$label)
```

```{r}
train = data
colnames(train)
```

```{r}
# Store predictors
personal = colnames(train)[3:6]
wrist_acc = colnames(train)[7:8]
chest_acc = colnames(train)[24:25]
wrist_bvp = colnames(train)[9:11]
wrist_eda = colnames(train)[12:17]
wrist_temp = colnames(train)[18:23]
wrist_physio = colnames(train)[9:23]
chest_ecg = colnames(train)[26:28]
chest_eda = colnames(train)[29:34]
chest_emg = colnames(train)[35:37]
chest_resp = colnames(train)[38:40]
chest_temp = colnames(train)[41:46]
chest_physio = colnames(train)[26:46]
all_wrist = colnames(train)[7:23]
all_chest = colnames(train)[24:46]
all_physio = colnames(train)[c(9:23,26:46)]
all_modalities = colnames(train)[c(7:46)]
```

```{r}
predictor_vars <- c("personal", "wrist_acc", "chest_acc", "wrist_bvp", "wrist_eda", "wrist_temp", "wrist_physio", "chest_ecg", "chest_eda", "chest_emg", "chest_resp", "chest_temp", "chest_physio", "all_wrist", "all_chest", "all_physio", "all_modalities")
```

# Model Selection

## Cross-Validation 

# Baseline

```{r}
cv <- data.frame(matrix(ncol = 16, nrow = 32))
colnames(cv) <- c("predictor", c(1:15))
cv$predictor <- c("wrist_acc", "wrist_acc", "chest_acc", "chest_acc", "wrist_bvp", "wrist_bvp", "wrist_eda", "wrist_eda", "wrist_temp", "wrist_temp", "wrist_physio", "wrist_physio", "chest_ecg", "chest_ecg", "chest_eda", "chest_eda", "chest_emg", "chest_emg", "chest_resp", "chest_resp", "chest_temp", "chest_temp", "chest_physio", "chest_physio", "all_wrist", "all_wrist", "all_chest", "all_chest", "all_physio", "all_physio", "all_modalities", "all_modalities")
```

```{r}
for(i in 1:1){
  for (j in 1:15){
    set.seed(1)
    test_sample = subset(data, id == j)
    predict_rf <- rep(0,nrow(test_sample))
    
    acc = mean(test_sample$label == predict_rf)*100
    auc = AUC(as.numeric(as.character(predict_rf)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# Subsample

## RF - no personal, we eventually choose this

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    test_sample = test

    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    acc = mean(test_sample$label == predict_rf)*100
    auc = AUC(as.numeric(as.character(predict_rf)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
# Check cv matrix
cv
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## RF - with personal

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    test_sample = test
    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(c(eval(parse(text = predictor_vars[1])), predictors), collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    acc = mean(test_sample$label == predict_rf)*100
    auc = AUC(as.numeric(as.character(predict_rf)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LDA - no personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_lda <- lda(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), data = train_sample)
    predict_lda <- predict(model_lda, test_sample)[[1]]
    acc = mean(test_sample$label == predict_lda)*100
    auc = AUC(as.numeric(as.character(predict_lda)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LDA - with personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_lda <- lda(as.formula(paste("label ~ ", paste(c(eval(parse(text = predictor_vars[1])), predictors), collapse = ' + '))), data = train_sample)
    predict_lda <- predict(model_lda, test_sample)[[1]]
    acc = mean(test_sample$label == predict_lda)*100
    auc = AUC(as.numeric(as.character(predict_lda)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LR - no personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_logistic <- glm(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), family=binomial(link='logit'), data = train_sample)
    predict_logistic <- predict(model_logistic, test_sample)
    predict_logistic <- ifelse(predict_logistic > 0.5,1,0)
    acc = mean(test_sample$label == predict_logistic)*100
    auc = AUC(as.numeric(as.character(predict_logistic)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LR - with personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_indices = sample(nrow(train), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_logistic <- glm(as.formula(paste("label ~ ", paste(c(eval(parse(text = predictor_vars[1])), predictors), collapse = ' + '))), family=binomial(link='logit'), data = train_sample)
    predict_logistic <- predict(model_logistic, test_sample)
    predict_logistic <- ifelse(predict_logistic > 0.5,1,0)
    acc = mean(test_sample$label == predict_logistic)*100
    auc = AUC(as.numeric(as.character(predict_logistic)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# Full 

## LDA - no personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_sample = train

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_lda <- lda(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), data = train_sample)
    predict_lda <- predict(model_lda, test_sample)[[1]]
    acc = mean(test_sample$label == predict_lda)*100
    auc = AUC(as.numeric(as.character(predict_lda)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LDA - with personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_sample = train

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_lda <- lda(as.formula(paste("label ~ ", paste(c(eval(parse(text = predictor_vars[1])), predictors), collapse = ' + '))), data = train_sample)
    predict_lda <- predict(model_lda, test_sample)[[1]]
    acc = mean(test_sample$label == predict_lda)*100
    auc = AUC(as.numeric(as.character(predict_lda)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LR - no personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_sample = train

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_logistic <- glm(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), family=binomial(link='logit'), data = train_sample)
    predict_logistic <- predict(model_logistic, test_sample)
    predict_logistic <- ifelse(predict_logistic > 0.5,1,0)
    acc = mean(test_sample$label == predict_logistic)*100
    auc = AUC(as.numeric(as.character(predict_logistic)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

## LR - with personal

```{r warning = FALSE}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train = subset(data, id != j)
    
    test_sample = test
    train_sample = train

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_logistic <- glm(as.formula(paste("label ~ ", paste(c(eval(parse(text = predictor_vars[1])), predictors), collapse = ' + '))), family=binomial(link='logit'), data = train_sample)
    predict_logistic <- predict(model_logistic, test_sample)
    predict_logistic <- ifelse(predict_logistic > 0.5,1,0)
    acc = mean(test_sample$label == predict_logistic)*100
    auc = AUC(as.numeric(as.character(predict_logistic)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# We select RF model, subsampling, no personal

# Variant 1 - Downsampling before subsampling

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train_sample = subset(data, id != j)
    test_sample = test

    train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
    train_indices = sample(nrow(train_sample), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    acc = mean(test_sample$label == predict_rf)*100
    auc = AUC(as.numeric(as.character(predict_rf)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# Variant 2 - Taking every 240th observation before subsampling

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train_sample = subset(data, id != j)
    test_sample = test
    train_sample <- train_sample[seq(1,nrow(train_sample),240),]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    acc = mean(test_sample$label == predict_rf)*100
    auc = AUC(as.numeric(as.character(predict_rf)), as.numeric(as.character(test_sample$label)))

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- auc
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# Chosen Model - RF, All Modalities, No Personal, Downsample, and then Subsample

## Confusion Matrix

```{r}
ret = data.table()
for (i in 1:15){
  test = subset(data, id == i)
  train_sample = subset(data, id != i)
  test_sample = test
  
  train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
  train_indices = sample(nrow(train_sample), 1000)
  train_sample = train[train_indices,]
  
  predictor = "all_modalities"
  predictors = eval(parse(text = predictor))
  model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
  predict_rf <- predict(model_rf, test_sample)
  cM <- confusionMatrix(data = predict_rf, reference = test_sample$label)
  if (i == 1){
    ret = cM$table
  }
  else {
    ret = ret + cM$table
  }
}
ret
```

## VI and tree plots
```{r}
tree_func <- function(final_model, 
                      tree_num) {
  
  # get tree by index
  tree <- randomForest::getTree(final_model, 
                                k = tree_num, 
                                labelVar = TRUE) %>%
    tibble::rownames_to_column() %>%
    # make leaf split points to NA, so the 0s won't get plotted
    mutate(`split point` = ifelse(is.na(prediction), `split point`, NA))
  
  # prepare data frame for graph
  graph_frame <- data.frame(from = rep(tree$rowname, 2),
                            to = c(tree$`left daughter`, tree$`right daughter`))
  
  # convert to graph and delete the last node that we don't want to plot
  graph <- graph_from_data_frame(graph_frame) %>%
    delete_vertices("0")
  
  # set node labels
  V(graph)$node_label <- gsub("_", " ", as.character(tree$`split var`))
  V(graph)$leaf_label <- as.character(tree$prediction)
  V(graph)$split <- as.character(round(tree$`split point`, digits = 2))
  
  # plot
  plot <- ggraph(graph, 'dendrogram') + 
    theme_bw() +
    geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = node_label), na.rm = TRUE, repel = TRUE) +
    geom_node_label(aes(label = split), vjust = 2.5, na.rm = TRUE, fill = "white") +
    geom_node_label(aes(label = leaf_label, fill = leaf_label), na.rm = TRUE, 
					repel = TRUE, colour = "white", fontface = "bold", show.legend = FALSE) +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          panel.background = element_blank(),
          plot.background = element_rect(fill = "white"),
          panel.border = element_blank(),
          axis.line = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(size = 18))
  
  return(plot)
}
```

```{r warning = FALSE}
set.seed(1)
predictor_vars = c("all_modalities", "wrist_physio", "all_wrist", "all_chest", "all_physio")
train_sample = data
train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
train_indices = sample(nrow(train_sample), 1000)
train_sample = train[train_indices,]
for (i in 1:length(predictor_vars)){
  predictor = predictor_vars[i]
  predictors = eval(parse(text = predictor))
  model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = TRUE, data = train_sample)
  cat("\n",predictor)
  print(importance(model_rf, type = 1))
  choices <- sample(500,5)
  for (i in 1:5){
    print(tree_func(final_model = model_rf, choices[i]))
  }
}

```

# Even more sensitivity analysis

```{r warning = FALSE}
set.seed(1)
predictor_vars = c("all_modalities")
train_sample = data
train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
train_indices = sample(nrow(train_sample), 1000)
train_sample = train[train_indices,]
for (i in 1:length(predictor_vars)){
  predictor = predictor_vars[i]
  predictors = eval(parse(text = predictor))
  model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = TRUE, mtry = 3, data = train_sample)
  cat("\n",predictor)
  print(importance(model_rf, type = 1))
  choices <- sample(500,5)
  for (i in 1:5){
    print(tree_func(final_model = model_rf, choices[i]))
  }
}
```
```{r warning = FALSE}
set.seed(1)
predictor_vars = c("all_modalities")
train_sample = data
train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
train_indices = sample(nrow(train_sample), 1000)
train_sample = train[train_indices,]
for (i in 1:length(predictor_vars)){
  predictor = predictor_vars[i]
  predictors = eval(parse(text = predictor))
  model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = TRUE, mtry = 9, data = train_sample)
  cat("\n",predictor)
  print(importance(model_rf, type = 1))
  choices <- sample(500,5)
  for (i in 1:5){
    print(tree_func(final_model = model_rf, choices[i]))
  }
}
```



# 3-class prediction

```{r}
load("final_data.rda")

new_data <- data.frame(new_data)
new_data <- subset(new_data, label != 4)

# Baseline = 0, stress = 1, amusement = 2
new_data$label[new_data$label == 1] <- 0
new_data$label[new_data$label == 2] <- 1
new_data$label[new_data$label == 3] <- 2 
new_data$label = as.factor(new_data$label)
data <- data.frame(new_data)
```

```{r}
nrow(subset(data, label == 0))/nrow(data)
nrow(subset(data, label == 1))/nrow(data)
nrow(subset(data, label == 2))/nrow(data)
```

```{r}
for(i in 1:1){
  for (j in 1:15){
    set.seed(1)
    test_sample = subset(data, id == j)
    predict_rf <- rep(0,nrow(test_sample))
    
    acc = mean(test_sample$label == predict_rf)*100
    predictions = as.numeric(as.character(predict_rf))
    actual = as.numeric(as.character(test_sample$label))
    predictions1 = predictions
    predictions2 = predictions
    predictions3 = predictions
    actual1 = actual
    actual2 = actual
    actual3 = actual
    # 0 is 1, 1 and 2 are 0
    predictions1[predictions1 == 1] <- 3
    predictions1[predictions1 == 2] <- 3
    predictions1[predictions1 == 0] <- 1
    predictions1[predictions1 == 3] <- 0
    actual1[actual1 == 1] <- 3
    actual1[actual1 == 2] <- 3
    actual1[actual1 == 0] <- 1
    actual1[actual1 == 3] <- 0  
    auc1 = AUC(predictions1, actual1)
    # 1 is 1, 0 and 2 are 0
    predictions2[predictions2 == 2] <- 0
    actual2[actual2 == 2] <- 0
    auc2 = AUC(predictions2, actual2)
    # 2 is 1, 0 and 1 are 0
    predictions3[predictions3 == 1] <- 0
    actual3[actual3 == 1] <- 0
    predictions3[predictions3 == 2] <- 1
    actual3[actual3 == 2] <- 1
    auc3 = AUC(predictions3, actual3)

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- mean(c(auc1, auc2, auc3))
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# RF Model

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train_sample = subset(data, id != j)
    test_sample = test

    train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
    train_indices = sample(nrow(train_sample), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    predictions = as.numeric(as.character(predict_rf))
    actual = as.numeric(as.character(test_sample$label))
    acc = mean(predictions == actual)*100
    predictions1 = predictions
    predictions2 = predictions
    predictions3 = predictions
    actual1 = actual
    actual2 = actual
    actual3 = actual
    # 0 is 1, 1 and 2 are 0
    predictions1[predictions1 == 1] <- 3
    predictions1[predictions1 == 2] <- 3
    predictions1[predictions1 == 0] <- 1
    predictions1[predictions1 == 3] <- 0
    actual1[actual1 == 1] <- 3
    actual1[actual1 == 2] <- 3
    actual1[actual1 == 0] <- 1
    actual1[actual1 == 3] <- 0  
    auc1 = AUC(predictions1, actual1)
    # 1 is 1, 0 and 2 are 0
    predictions2[predictions2 == 2] <- 0
    actual2[actual2 == 2] <- 0
    auc2 = AUC(predictions2, actual2)
    # 2 is 1, 0 and 1 are 0
    predictions3[predictions3 == 1] <- 0
    actual3[actual3 == 1] <- 0
    predictions3[predictions3 == 2] <- 1
    actual3[actual3 == 2] <- 1
    auc3 = AUC(predictions3, actual3)

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- mean(c(auc1, auc2, auc3))
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# 4-class prediction

```{r}
load("final_data.rda")

new_data <- data.frame(new_data)

new_data$label[new_data$label == 1] <- 0
new_data$label[new_data$label == 2] <- 1
new_data$label[new_data$label == 3] <- 2
new_data$label[new_data$label == 4] <- 3 

new_data$label = as.factor(new_data$label)
data <- data.frame(new_data)
```

```{r}
nrow(subset(data, label == 0))/nrow(data)
nrow(subset(data, label == 1))/nrow(data)
nrow(subset(data, label == 2))/nrow(data)
nrow(subset(data, label == 3))/nrow(data)
```

# Baseline

```{r}
for(i in 1:1){
  for (j in 1:15){
    set.seed(1)
    test_sample = subset(data, id == j)
    predict_rf <- rep(0,nrow(test_sample))
    
    acc = mean(test_sample$label == predict_rf)*100
    predictions = as.numeric(as.character(predict_rf))
    actual = as.numeric(as.character(test_sample$label))
    predictions1 = predictions
    predictions2 = predictions
    predictions3 = predictions
    predictions4 = predictions
    actual1 = actual
    actual2 = actual
    actual3 = actual
    actual4 = actual
    # 0 is 1, 1 and 2 and 3 are 0
    predictions1[predictions1 == 1] <- 3
    predictions1[predictions1 == 2] <- 3
    predictions1[predictions1 == 0] <- 1
    predictions1[predictions1 == 3] <- 0
    actual1[actual1 == 1] <- 3
    actual1[actual1 == 2] <- 3
    actual1[actual1 == 0] <- 1
    actual1[actual1 == 3] <- 0  
    auc1 = AUC(predictions1, actual1)
    # 1 is 1, 0 and 2 and 3 are 0
    predictions2[predictions2 == 2] <- 0
    predictions2[predictions2 == 3] <- 0
    actual2[actual2 == 2] <- 0
    actual2[actual2 == 3] <- 0
    auc2 = AUC(predictions2, actual2)
    # 2 is 1, 0 and 1 and 3 are 0
    predictions3[predictions3 == 1] <- 0
    predictions3[predictions3 == 3] <- 0
    predictions3[predictions3 == 2] <- 1
    actual3[actual3 == 1] <- 0
    actual3[actual3 == 3] <- 0
    actual3[actual3 == 2] <- 1
    auc3 = AUC(predictions3, actual3)
    # 3 is 1, 0 and 1 and 2 are 0
    predictions4[predictions4 == 1] <- 0
    predictions4[predictions4 == 2] <- 0
    predictions4[predictions4 == 3] <- 1
    actual4[actual4 == 1] <- 0
    actual4[actual4 == 2] <- 0
    actual4[actual4 == 3] <- 1
    auc4 = AUC(predictions4, actual4)    
    

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- mean(c(auc1, auc2, auc3, auc4))
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```

# RF Model

```{r}
for(i in 1:16){
  for (j in 1:15){
    set.seed(1)
    test = subset(data, id == j)
    train_sample = subset(data, id != j)
    test_sample = test

    train_sample <- downSample(train_sample[,-c(2)], train_sample[,c(2)], list = FALSE, yname = "label")
    train_indices = sample(nrow(train_sample), 1000)
    train_sample = train[train_indices,]

    predictor = cv$predictor[(i-1)*2+1]
    predictors = eval(parse(text = predictor))
    model_rf <- randomForest(as.formula(paste("label ~ ", paste(predictors, collapse = ' + '))), ntree = 500, importance = FALSE, data = train_sample)
    predict_rf <- predict(model_rf, test_sample)
    predictions = as.numeric(as.character(predict_rf))
    actual = as.numeric(as.character(test_sample$label))
    acc = mean(predictions == actual)*100
    predictions1 = predictions
    predictions2 = predictions
    predictions3 = predictions
    predictions4 = predictions
    actual1 = actual
    actual2 = actual
    actual3 = actual
    actual4 = actual
    # 0 is 1, 1 and 2 and 3 are 0
    predictions1[predictions1 == 1] <- 3
    predictions1[predictions1 == 2] <- 3
    predictions1[predictions1 == 0] <- 1
    predictions1[predictions1 == 3] <- 0
    actual1[actual1 == 1] <- 3
    actual1[actual1 == 2] <- 3
    actual1[actual1 == 0] <- 1
    actual1[actual1 == 3] <- 0  
    auc1 = AUC(predictions1, actual1)
    # 1 is 1, 0 and 2 and 3 are 0
    predictions2[predictions2 == 2] <- 0
    predictions2[predictions2 == 3] <- 0
    actual2[actual2 == 2] <- 0
    actual2[actual2 == 3] <- 0
    auc2 = AUC(predictions2, actual2)
    # 2 is 1, 0 and 1 and 3 are 0
    predictions3[predictions3 == 1] <- 0
    predictions3[predictions3 == 3] <- 0
    predictions3[predictions3 == 2] <- 1
    actual3[actual3 == 1] <- 0
    actual3[actual3 == 3] <- 0
    actual3[actual3 == 2] <- 1
    auc3 = AUC(predictions3, actual3)
    # 3 is 1, 0 and 1 and 2 are 0
    predictions4[predictions4 == 1] <- 0
    predictions4[predictions4 == 2] <- 0
    predictions4[predictions4 == 3] <- 1
    actual4[actual4 == 1] <- 0
    actual4[actual4 == 2] <- 0
    actual4[actual4 == 3] <- 1
    auc4 = AUC(predictions4, actual4)    
    

    cv[(i-1)*2+1,j+1] <- acc
    cv[(i-1)*2+2,j+1] <- mean(c(auc1, auc2, auc3, auc4))
  }
}
```

```{r}
# Get Means and standard deviations
rowMeans(cv[,c(2:16)])
rowSds(as.matrix(cv[,c(2:16)]))
```
